### 2018-07-29 Sections/essay_quantcoin.tex
Essays reformat

\subsection{The quantum future of cryptocurrencies}\index{Computation-backed currency}\index{Cryptocurrency}\index{QuantCoin\texttrademark}\label{sec:quant_coin_essay}

>>>>

\section{The quantum future of cryptocurrencies}\index{Computation-backed currency}\index{Cryptocurrency}\index{QuantCoin\texttrademark}\label{sec:quant_coin_essay}

### 2018-07-29 Sections/essay_security_implications_of_the_global_quantum_internet.tex
Economics, minor stuff, latin quotes
Figure reformatting to make double column, rather than stacked
mdframed
Added all dropcaps
Essays reformat

\subsection{Security implications of the global quantum internet} \label{sec:sec_imp} \index{Security implications}

With any new technology comes ethical considerations. Who will have access to it, and how do they plan to use it? For this reason, many developed nations have export bans or restrictions in place on `dual-use' technologies -- those which have clearly legitimate and morally justifiable uses, but also nefarious ones by competitors and criminals. Nuclear technology is the obvious archetype. Quantum technologies (in particular quantum computing and quantum cryptography) are particularly vulnerable to dual-use, and for this reason are becoming subject to dual-use technology legislation, such as export controls, in some nations. In Australia, for example, legislation is being introduced criminalising the transfer of knowledge on certain quantum and cryptographic technologies to foreign nationals of certain target countries.

@@

\renewcommand{\tablename}{ALG.}

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function MakeAmericaGreatAgain(Putin):
\begin{enumerate}
    \item A Russian bedroom hacker with no direct access to quantum technology, delegates a factorisation algorithm to the cloud using homomorphic encryption.
    \item The computation is physically executed on a server in the United States.
    \item The result is returned to our Russian comrade.
    \item The Russian uses the obtained private RSA key to hack Hillary's emails.
    \item The emails are strategically leaked during the next Presidential election.
    \item This swings the election in favour of Trump\texttrademark.
    \item The NSA and FBI have no clue who was behind it, since it was homomorphically encrypted.
    \item They blame Edward Snowden.
    \item Fox News\texttrademark\,calls for his execution.
    \item They'd kick themselves if they found out the algorithm was actually executed on US soil.
    \item Unless the NSA switches off the entire quantum internet, they can't prevent it from happening again in subsequent elections.
    \item return(America is Great Again\texttrademark).
    \item $\Box$
\end{enumerate}}}}
\caption{A typical example of a nefarious use for cloud quantum computation. See Fig.~\ref{fig:trump_tweet} for the outcome.} \label{alg:russian}\index{Trump}\index{Covfefe}
\end{table}

@@

\latinquote{Annus horribilis.}

>>>>

%
% Security Implications of the Global Quantum Internet
%

\section{Security implications of the global quantum internet} \label{sec:sec_imp} \index{Security implications}

\dropcap{W}{ith} any new technology comes ethical considerations. Who will have access to it, and how do they plan to use it? For this reason, many developed nations have export bans or restrictions in place on `dual-use' technologies -- those which have clearly legitimate and morally justifiable uses, but also nefarious ones by competitors and criminals. Nuclear technology is the obvious archetype. Quantum technologies (in particular quantum computing and quantum cryptography) are particularly vulnerable to dual-use, and for this reason are becoming subject to dual-use technology legislation, such as export controls, in some nations. In Australia, for example, legislation is being introduced criminalising the transfer of knowledge on certain quantum and cryptographic technologies to foreign nationals of certain target countries.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function MakeAmericaGreatAgain(Putin):
\begin{enumerate}
    \item A Russian bedroom hacker with no direct access to quantum technology, delegates a factorisation algorithm to the cloud using homomorphic encryption.
    \item The computation is physically executed on a server in the United States.
    \item The result is returned to our Russian comrade.
    \item The Russian uses the obtained private RSA key to hack Hillary's emails.
    \item The emails are strategically leaked during the next Presidential election.
    \item This swings the election in favour of Trump\texttrademark.
    \item The NSA and FBI have no clue who was behind it, since it was homomorphically encrypted.
    \item They blame Edward Snowden.
    \item Fox News\texttrademark\,calls for his execution.
    \item They'd kick themselves if they found out the algorithm was actually executed on US soil.
    \item Unless the NSA switches off the entire quantum internet, they can't prevent it from happening again in subsequent elections.
    \item return(America is Great Again\texttrademark).
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{A typical example of a nefarious use for cloud quantum computation. See Fig.~\ref{fig:trump_tweet} for the outcome.} \label{alg:russian}\index{Trump}\index{Covfefe}
\end{table}

@@

### 2018-07-29 Sections/essay_the_era_of_quantum_supremacy.tex
Added all dropcaps
Essays reformat

\subsection{The era of quantum supremacy} \label{sec:era_quant} \index{Quantum supremacy}

A pertinent question to ask is `What is the timescale for useful quantum technologies? When will they be viable?'. The correct answer is likely very soon.

>>>>

\section{The era of quantum supremacy} \label{sec:era_quant} \index{Quantum supremacy}

\dropcap{A}{} pertinent question to ask is `What is the timescale for useful quantum technologies? When will they be viable?'. The correct answer is likely very soon.
